---
title: "Cross check E2 with hadron"
author: "Marco Garofalo"
date: "2/9/2021"
output: html_document
---

```{r setup, include=FALSE}

```

## Opening the file and loading libraries

```{r }
library(hadron)
if(!exists("foo", mode="function")) source("read_header.R")

to.read = file("/home/marco/analysis/phi4/tuning_masses/G2t_T128_L20_msq0-4.925000_msq1-4.850000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_merged_bin10000", "rb")

```

## Read the header

```{r}
header<-read_header(to.read)
header
```

## Reading the configuration 

We read the configuration from the file in to the three dimensional array d

```{r}
configurations <- list()
d<-array(dim = c(header$ncorr, header$L[1], header$confs) )

for (iconf in  c(1:header$confs)){
  configurations<-append(configurations, readBin(to.read, integer(),n = 1, endian = "little"))
  for(t in c(1:header$L[1] ) ){
    for (corr in  c(1:header$ncorr)){
          d[corr, t, iconf]<-readBin(to.read, double(),n = 1, endian = "little")
      }
  }
}
```

## construct the cf container



here we select the correlator n=1
$$\langle \phi_0(t) \phi_0(0)\rangle$$

 
```{r}
n<-1

mycf <- cf_meta(nrObs =1, Time = header$L[1], nrStypes = 1)
mycf <- cf_orig(mycf, cf = t(d[n, ,]))
mycf <- symmetrise.cf(mycf, sym.vec = c(1))
# Bootstrap cf
boot.R <- 150
boot.l <- 1
seed <- 1433567
cfb <- bootstrap.cf(cf=mycf, boot.R=boot.R, boot.l=boot.l, seed=seed)


```


## Single particle energy

here we are plotting the "log" effective mass $\log c(t)/c(t+1)$
```{r, warning=FALSE}


log_meff <-bootstrap.effectivemass(cfb, type='log')
plot(log_meff)

```

## Two particel energy

 Here we select the correlator n=3 
 $$
 \langle\phi_0(t)^2 \phi_0(0)^2 \rangle
 $$
```{r}
n<-3

mycf <- cf_meta(nrObs =1, Time = header$L[1], nrStypes = 1)
mycf <- cf_orig(mycf, cf = t(d[n, ,]))
mycf <- symmetrise.cf(mycf, sym.vec = c(1))
# Bootstrap cf
boot.R <- 150
boot.l <- 1
seed <- 1433567
cfb <- bootstrap.cf(cf=mycf, boot.R=boot.R, boot.l=boot.l, seed=seed)

```

The plot of the effective mass is not what we expected, ignoring finite T pollution this should be a constant as in the case of one particle.

```{r}
  log_meff <-bootstrap.effectivemass(cfb, type='log')
  plot(log_meff)
```

The shifted effective mass instead looks fine

```{r}
  scf<-removeTemporal.cf(cfb)
  shifted_log_meff <-bootstrap.effectivemass(scf, type='shifted')
  plot(shifted_log_meff)
```


# Two different particle energy 

 Here we select the correlator n=12
 $$
 \langle\phi_0(t)\phi_1(t) \phi_0(0)\phi_1(0) \rangle   
 $$
```{r, warning=FALSE}
n<-12

mycf <- cf_meta(nrObs =1, Time = header$L[1], nrStypes = 1)
mycf <- cf_orig(mycf, cf = t(d[n, ,]))
mycf <- symmetrise.cf(mycf, sym.vec = c(1))
# Bootstrap cf
boot.R <- 150
boot.l <- 1
seed <- 1433567
cfb <- bootstrap.cf(cf=mycf, boot.R=boot.R, boot.l=boot.l, seed=seed)
log_meff <-bootstrap.effectivemass(cfb, type='log')
plot(log_meff)

```


```{r}
n_00<-3
n_11<-4
n_01<-12
mycf<- cf()
for (n in c(n_00,n_11,n_01)){
  cf_tmp <- cf_meta(nrObs =1, Time = header$L[1], nrStypes = 1)
  cf_tmp <- cf_orig(cf_tmp, cf = t(d[n, ,]))
  cf_tmp <- symmetrise.cf(cf_tmp, sym.vec = c(1))
  mycf<- c(mycf, cf_tmp)
}
# Bootstrap cf
boot.R <- 150
boot.l <- 1
seed <- 1433567
cfb <- bootstrap.cf(cf=mycf, boot.R=boot.R, boot.l=boot.l, seed=seed)

cf_new<- cfb$cf/sqrt(cfb$cf*cfb$cf)

plot(cf_new)

```


# T48

```{r}

to.read = file("/home/marco/analysis/phi4/tuning_masses/G2t_T48_L20_msq0-4.925000_msq1-4.850000_l02.500000_l12.500000_mu5.000000_g0.000000_rep1_bin10000", "rb")
header<-read_header(to.read)
configurations <- list()
d<-array(dim = c(header$ncorr, header$L[1], header$confs) )

for (iconf in  c(1:header$confs)){
  configurations<-append(configurations, readBin(to.read, integer(),n = 1, endian = "little"))
  for(t in c(1:header$L[1] ) ){
    for (corr in  c(1:header$ncorr)){
          d[corr, t, iconf]<-readBin(to.read, double(),n = 1, endian = "little")
      }
  }
}
n<-3

mycf <- cf_meta(nrObs =1, Time = header$L[1], nrStypes = 1)
mycf <- cf_orig(mycf, cf = t(d[n, ,]))
mycf <- symmetrise.cf(mycf, sym.vec = c(1))
# Bootstrap cf
boot.R <- 150
boot.l <- 1
seed <- 1433567
cfb <- bootstrap.cf(cf=mycf, boot.R=boot.R, boot.l=boot.l, seed=seed)
 log_meff <-bootstrap.effectivemass(cfb, type='log')
  plot(log_meff)


```
