---
title: "gplots"
author: "MG"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
    latex_engine: xelatex
vignette: "%\\VignetteIndexEntry{gplots} %\\VignetteEngine{knitr::rmarkdown} \\usepackage[utf8]{inputenc}
  \ \n"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.align='center',       comment='')
knitr::opts_chunk$set(fig.width=6, fig.height=4) 
require(ggplot2)
require(scales) # to access break formatting functions
library(latex2exp)
library(pander)
panderOptions('knitr.auto.asis', FALSE)
```

The plots for each ensemble are

-   effective mass meff0 from $\langle \phi_0(t) \phi_0(0)\rangle$

-   effective mass meff1 from $\langle \phi_1(t) \phi_1(0)\rangle$

    -   meff is extracted fitting the correlator as $$
         c_1(t)=|A_{1-0}|^2 \exp(-M \frac{T}{2}) \cosh\left(M (t-\frac{T}{2})\right) 
         $$

-   Two particle energy for $\langle \phi_0^2(t) \phi_0^2(0)\rangle$

-   Two particle energy for $\langle \phi_1^2(t) \phi_1^2(0)\rangle$

-   Two particle energy for $\langle \phi^2(t) \phi^{*2}(0)\rangle$

    -   The two particle energy $E_2$ is extracted from the correlator
        $$
        c_2(t)=|A_{2-0}|^2 \exp(-E_2 \frac{T}{2}) \cosh\left(E_2 (t-\frac{T}{2})\right)+
        |A_{1-1}|^2 \exp(-M T).
         $$ to remove the extra term $|A_{1-1}|^2 \exp(-M T)$ we take
        the difference $$
        \tilde{c}_2(t)=c(t)-c(t+1)=|A_{2-0}|^2 \exp(-E_2 \frac{T}{2}) \sinh\left(E_2 (t-\frac{T-1}{2})\right).
         $$ The third correlator is constructed with the complex field\
        $$
        \phi=\phi_0+i\phi_1
         $$

-   Two particle energy for $\langle \phi_0^3(t) \phi_0^3(0)\rangle$

-   Two particle energy for $\langle \phi_1^3(t) \phi_1^3(0)\rangle$

-   Two particle energy for $\langle \phi^3(t) \phi^{*3}(0)\rangle$

    -   The three particle energy $E_3$ is extracted from the correlator
        $$
        c_3(t)=|A_{3-0}|^2 \exp(-E_3 \frac{T}{2}) \cosh\left(E_3 (t-\frac{T}{2})\right)+\\
        |A_{2-1}|^2 \exp(-(E_2+M) \frac{T}{2}) \cosh\left((E_2-M) (t-\frac{T}{2})\right).
         $$

-   BH four point function
    $\langle \phi_0(\frac{T}{2})\phi_0(t)\phi_0(\frac{T}{8}) \phi_0(0)\rangle$

-   BH four point function
    $\langle \phi_1(\frac{T}{2})\phi_1(t)\phi_1(\frac{T}{8}) \phi_1(0)\rangle$

-   BH four point function
    $$C_4^{BH}=\frac{\langle \phi_0(\frac{T}{2})\phi_1(t)\phi_1(\frac{T}{8}) \phi_0(0)\rangle}
    {\langle \phi_0(\frac{T}{2}) \phi_0(0)\rangle \langle \phi_1(t)\phi_1(\frac{T}{8}) \rangle} -1$$

```{r  echo=FALSE, results="asis",code=readLines("ggplot.R")}
```

# Masses

```{r echo=FALSE}
kable(df[,c(1,2,7,8,3,4,5,6)])

library(tidyr)
#
#df1 <- gather(df, key = measure, value = Rate, 
#c("meff0", "meff1"))
#gg <- ggplot(df1, aes(x=msq0, y = Rate, group = measure, colour = measure))+ geom_point()
colors <- c("meff0" = "blue", "meff1" = "red")


gg <- ggplot(df, aes(x=msq0, y=meff0,color ="meff0", shape=as.factor(L ) )) + geom_point(size=3) 
gg <- gg +geom_errorbar(aes(ymin=meff0-Emeff0, ymax=meff0+Emeff0,  color="meff0"), width=0.003)  
gg <- gg+ geom_point( aes(x=msq0, y=meff1, color="meff1", shape=as.factor(L)  ),size=3 ) 
gg <- gg +geom_errorbar(aes(ymin=meff1-Emeff1, ymax=meff1+Emeff1 , color="meff1"),  width = 0.003)  
gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)


gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$m_{eff}$') )


gg <- gg+theme_bw()

plot(gg)

```

```{r}

colors <- c("meff0" = "blue", "meff1" = "red")

gg <- ggplot(df, aes(x=msq0, y=meff0,color =as.factor(L), shape=as.factor(msq1) )) + geom_point(size=3) 
#gg <- gg +geom_errorbar(aes(x=msq0, ymin=meff0-Emeff0, ymax=meff0+Emeff0), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$m_{eff}$') )
gg <- gg+theme_bw()

plot(gg)
```

```{r}

colors <- c("meff0" = "blue", "meff1" = "red")

gg <- ggplot(df, aes(x=msq0, y=meff1,color =as.factor(L), shape=as.factor(msq1) )) + geom_point(size=3) 
#gg <- gg +geom_errorbar(aes(x=msq0, ymin=meff0-Emeff0, ymax=meff0+Emeff0), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$m_{eff}$') )
gg <- gg+theme_bw()

plot(gg)
```

# Two particle energy

```{r echo=FALSE}
kable(df[,c(1,2,7,8,14,15,16,17,18,19)])

library(tidyr)

colors <- c("E2_0" = "blue", "E2_1" = "red", "E2"="black")


gg <- ggplot(df, aes(x=msq0, y=E2_0,color ="E2_0")) + geom_point() 
gg <- gg +geom_errorbar(aes(ymin=E2_0-E2_0err, ymax=E2_0+E2_0err,  color="E2_0"), width=0.005)  
gg <- gg+ geom_point( aes(x=msq0, y=E2_1, color="E2_1")) 
gg <- gg +geom_errorbar(aes(ymin=E2_1-E2_1err, ymax=E2_1+E2_1err , color="E2_1"),  width = 0.005)  
gg <- gg+ geom_point( aes(x=msq0, y=E2, color="E2")) 
gg <- gg +geom_errorbar(aes(ymin=E2-E2err, ymax=E2+E2err , color="E2"),  width = 0.005) 
gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)


gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$E2$') )


gg <- gg+theme_bw()

plot(gg)

```

# Three particle energy

```{r echo=FALSE}
kable(df[,c(1,2,7,8,20,21,22,23,24,25)])

library(tidyr)

colors <- c("E3_0" = "blue", "E3_1" = "red", "E3"="black")


gg <- ggplot(df, aes(x=msq0, y=E3_0,color ="E3_0")) + geom_point() 
gg <- gg +geom_errorbar(aes(ymin=E3_0-E3_0err, ymax=E3_0+E3_0err,  color="E3_0"), width=0.005)  
gg <- gg+ geom_point( aes(x=msq0, y=E3_1, color="E3_1")) 
gg <- gg +geom_errorbar(aes(ymin=E3_1-E3_1err, ymax=E3_1+E3_1err , color="E3_1"),  width = 0.005)  
gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)

gg <- gg+ geom_point( aes(x=msq0, y=E3, color="E3")) 
gg <- gg +geom_errorbar(aes(ymin=E3-E3err, ymax=E3+E3err , color="E3"),  width = 0.005) 
gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)


gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$E3$') )


gg <- gg+theme_bw()

plot(gg)

```

# Ampitude BH

```{r echo=FALSE}

kable(df[,c(1,2,7,8,30,31)])

gg <- ggplot(df, aes(x=msq0, y=a_01,color =as.factor(L), shape=as.factor(msq1) )) + geom_point(size=3) 
gg <- gg +geom_errorbar(aes(x=msq0, ymin=a_01-a_01err, ymax=a_01+a_01err), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('a m_0^2'), y= TeX('$a_{N\\pi}$') )
gg <- gg+theme_bw()

plot(gg)
```

# to be compared with the result of the paper <https://arxiv.org/abs/1806.02367>

```{r echo=FALSE}
paper_table <- read.table("paper_data.txt",fill = TRUE , blank.lines.skip=TRUE,skip=0)
kable(paper_table)
```
