---
title: "Untitled"
author: "Marco Garofalo"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require("gplots")

library(ggplot2)
library(plotly)
library(tidyverse)
library(htmlwidgets)
library(pander)
library(latex2exp)
library(knitr)
library(dplyr) #data frame manipulation
require(scales) # to access break formatting functions
library(shiny)
library(shinyWidgets)
library(ggrepel)

library(pander)
panderOptions('knitr.auto.asis', FALSE)

library(Rose)
#source("./Rread_block.R")
#library("Rose")
```

```{r ,include=FALSE}
  #######################################################################################
    #symmary table
    ####################################################################################### 
    df_tot_compact<- data.frame(  "L"=c(0),"T"=c(0),
                                  "msq0"=c(0), "msq1"=c(0),
                                  "meff0"=c(0),  "meff1"=c(0) , 
                                  #   "E2_0"=c(0),  "E2_1"=c(0),
                                  #   "E3_0"=c(0),  "E3_1"=c(0),
                                  "a_01_BH"=c(0),
                                  "a_01_luscher"=c(0) ,"E2_01"=c(0) ,"DeltaE2_01"=c(0) ,
                                  "lambda0"=c(0) , "lambda1"=c(0),
                                  "mu"=c(0), "g"=c(0), "rep"=c(0)  
                                  ,"a_0_luscher"=c(0) ,"E2_0"=c(0) ,"DeltaE2_0"=c(0) 
                                  ,"a_1_luscher"=c(0) ,"E2_1"=c(0) ,"DeltaE2_1"=c(0) 
                                  ,"a_01_BH_c"=c(0) , "muDE2"=c(0),
                                  "a_01_m0_m1"=c(0), "a_00_m0"=c(0),"muDE2_0"=c(0))

     df<- data.frame(  "L"=c(0),"T"=c(0),
                                  "msq0"=c(0), "msq1"=c(0),
                                  "meff0"=c(0),"meff0_err"=c(0),  "meff1"=c(0) ,
                                  "meff1_err"=c(0) ,
                                  "a_01_BH"=c(0),"a_01_BH_err"=c(0),
                                  "a_01_luscher"=c(0),"a_01_luscher_err"=c(0) ,
                                  "E2_01"=c(0) ,"E2_01_err"=c(0) 
                                   ,"DeltaE2_01"=c(0),"DeltaE2_01_err"=c(0) 
                                  ,"lambda0"=c(0) , "lambda1"=c(0),
                                  "mu"=c(0), "g"=c(0), "rep"=c(0) , 
                                  "a_0_luscher"=c(0),"a_0_luscher_err"=c(0) ,
                       "E2_0"=c(0) ,"E2_0_err"=c(0) ,"DeltaE2_0"=c(0) ,"DeltaE2_0_err"=c(0) 
                                  ,"a_1_luscher"=c(0) ,"a_1_luscher_err"=c(0) ,
                       "E2_1"=c(0) ,"E2_1_err"=c(0) ,"DeltaE2_1"=c(0),"DeltaE2_1_err"=c(0)
                       ,"a_01_BH_c"=c(0) ,"a_01_BH_c_err"=c(0)
                       , "muDE2"=c(0), "muDE2_err"=c(0)
                       ,"a_01_m0_m1"=c(0),"a_01_m0_m1_err"=c(0)
                       ,"a_00_m0"=c(0),"a_00_m0err"=c(0)
                       , "muDE2_0"=c(0), "muDE2_0_err"=c(0)  )
     
    count<-1
    for (dir in c( "Data" )){
        #for (dir in c( "Data" )){  
        for (msq1 in c(-4.85)){
            for (msq0 in c(-4.925)){
                for (l0 in c(2.5)){  
                    for (l1 in c(2.5)){    
                        for (mu in c(5.0)){    
                            for (g in c(0)){
                                #for (L in c(10,16,20,24,40)){
                                  #for (L in c(10,16,20,24,32)){
                                    for (L in c(20,24,32)){
                                    #for (T in c(24,32,48,128)){
                                      for (T in c(32,128,48)){
                                        for (rep in c(0)){
                                            file1=sprintf("%s/G2t_T%d_L%d_msq0%.6f_msq1%.6f_l0%.6f_l1%.6f_mu%.6f_g%.6f_rep%d_output",
                                                          dir,T,L,msq0,msq1,l0,l1,mu,g,rep)
                                            if (file.exists(file1)){
                                                
                                                
                                                
                                                columns_file<-c(1:20)  
                                                mylist<- list(  L,T)
                                                mylist  <-append(mylist, list(msq0, msq1 ))
                                                dflist<- list(L,T,msq0,msq1)
                                                
                                                mt<-read_df(file1)
                                                
                                                fit<- get_fit_n(mt,2)
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                fit<- get_fit_n(mt,3)
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2]))
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                #E2
                                                fit<- get_fit_n(mt,3)
                                                #mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                fit<- get_fit_n(mt,5)
                                                #mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                
                                                #E3
                                                fit<- get_fit_n(mt,7)
                                                #mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                fit<- get_fit_n(mt,8)
                                                #mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                
                                                #a_BH
                                                fit<- get_fit_n(mt,13)
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2]))
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                #a_lusher, E2,deltaE2   
                                                fit<- get_fit_n(mt,20)
                                                mylist  <- append(mylist, mean_print(fit[2,1], fit[2,2]) )
                                                dflist<- append(dflist, list(fit[2,1], fit[2,2]))
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                mylist  <- append(mylist, mean_print(fit[2,3], fit[2,4]))
                                                dflist<- append(dflist, list(fit[2,3], fit[2,4]))
                                                
                                                mylist  <-append(mylist, list( l0,l1,mu,g,rep ))
                                                dflist<- append(dflist, list( l0,l1,mu,g,rep ))
                                                #a_0_lusher, E2_0,deltaE2_0   
                                                fit<- get_fit_n(mt,5)
                                                mylist  <- append(mylist, mean_print(fit[2,1], fit[2,2]) )
                                                dflist<- append(dflist, list(fit[2,1], fit[2,2]))
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                mylist  <- append(mylist, mean_print(fit[2,3], fit[2,4]))
                                                dflist<- append(dflist, list(fit[2,3], fit[2,4]))
                                                
                                                
                                                #a_1_lusher, E2_1,deltaE2_1   
                                                fit<- get_fit_n(mt,6)
                                                mylist  <- append(mylist, mean_print(fit[2,1], fit[2,2]) )
                                                dflist<- append(dflist, list(fit[2,1], fit[2,2]))
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2])) 
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                                mylist  <- append(mylist, mean_print(fit[2,3], fit[2,4]))
                                                dflist<- append(dflist, list(fit[2,3], fit[2,4]))
                                                
                                                
                                                #a_BH+c
                                                fit<- get_fit_n(mt,18)
                                                mylist  <- append(mylist, mean_print(fit[1,1], fit[1,2]))
                                                dflist<- append(dflist, list(fit[1,1], fit[1,2]))
                                             
                                                
                                                #muDE2
                                                fit<- get_fit_n(mt,20)
                                                mylist  <- append(mylist, mean_print(fit[2,7], fit[2,8]) )
                                                dflist<- append(dflist, list(fit[2,7], fit[2,8]))
                                                
                                                
                                                #a_01*(m0+m1)
                                                fit<- get_fit_n(mt,20)
                                                mylist  <- append(mylist, mean_print(fit[2,9], fit[2,10]) )
                                                dflist<- append(dflist, list(fit[2,9], fit[2,10]))
                                                #a_0*(m0)
                                                fit<- get_fit_n(mt,5)
                                                mylist  <- append(mylist, mean_print(fit[2,9], fit[2,10]) )
                                                dflist<- append(dflist, list(fit[2,9], fit[2,10]))
                                                
                                                #muDE2_0
                                                fit<- get_fit_n(mt,5)
                                                mylist  <- append(mylist, mean_print(fit[2,7], fit[2,8]) )
                                                dflist<- append(dflist, list(fit[2,7], fit[2,8]))
                          
                                                df_tot_compact[count,] <-mylist
                                                df[count,] <-dflist
                                                count<- count+1
                                                
                                            }
                                            
                                        }}}}}}}}}}
    
  
    


```

## Masses


```{r , echo=FALSE}


kable(df_tot_compact[,c("L","T","meff0","meff1","E2_01","DeltaE2_01","a_01_luscher") ])

gg <- ggplot(df, aes(x=L, y=meff0 ,label=T )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes(x=L, ymin=meff0-meff0_err, ymax=meff0+meff0_err), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$m_{eff0}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

plot(gg)

gg <- ggplot(df, aes(x=L, y=meff1 ,label=T )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes(x=L, ymin=meff1-meff1_err, ymax=meff1+meff1_err), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$m_{eff1}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

plot(gg)
```

## Two particle energy and scattering length with Luscher method

$$
\langle \phi_0\phi_1 (t)  \phi_0\phi_1(0) \rangle= |A_{N\pi\to0}| \left(e^{-tE_{N\pi} }+ e^{-(T-t)E_{N\pi} }\right)+
|A_{\pi\to N}|^2  \left(e^{-TE_\pi -tE_{N}+tE_\pi }+ e^{-TE_N -tE_{\pi}+tE_N  }\right)
$$
$$
\Delta E_2=E2_{01}-m_{meff0}-m_{meff1} = -\frac{2\pi a }{\mu_{12}L^3}\left[1+c_1 \frac{a}{L}+c_2\left(\frac{a}{L}\right)^2\right]+ O\left(\frac{1}{L^6}\right)
$$

```{r ,echo=FALSE, warning=FALSE,results='asis'}

#kable(df_tot_compact[,c("L","T","E2_01","msq1","meff0","meff1") ])

gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=E2_01,label=T  )  ) + geom_point(size=2) 

gg <- gg +geom_errorbar(aes( ymin=E2_01-E2_01_err, ymax=E2_01+E2_01_err), width=0.002)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$E2_{01}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

plot(gg)


gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=a_01_luscher,label=T  )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes( ymin=a_01_luscher-a_01_luscher_err, ymax=a_01_luscher+a_01_luscher_err), color="blue", width=0.2)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$a_{hl}^{luscher}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

gg<- gg+geom_text_repel()+theme(axis.text=element_text(size=12), axis.title=element_text(size=17,face="bold"))

plot(gg)
pdf("a_01_luscher.pdf", width = 8, height = 5)
plot(gg)
dev.off()

```

## Fitting all data

```{r,echo=FALSE}
xx<-df[,"L"]
yy<-df[,"muDE2"]*df[,"L"]^3
dy<-df[,"muDE2_err"]*df[,"L"]^3
c1<- -2.837297
c2<- 6.375183

wnlmod <- nls(yy ~ -(2*pi *a)*(1+c1*a/xx+c2*(a/xx)^2) , start = list(a = 1), weights = dy^-2)
res<-summary(wnlmod)$coefficients
kable(res)
gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=muDE2*L^3,label=T  )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes( ymin=(muDE2-muDE2_err)*L^3, ymax=(muDE2+muDE2_err)*L^3, width=0.002)  ,color="blue", width=0.2)  
dx<-data.frame(xx=seq(min(df[,"L"]-2),max(df[,"L"]+2), length.out=50   ))
dx$v<-predict(wnlmod, newdata = dx)
gg <- gg+ geom_line(data=dx, aes(x=xx, y=v  ))
#gg <- gg+lines(xx, predict(wnlmod), col = "red")
gg <- gg+ labs(x = TeX('L'), y= TeX('$L^3\\mu_{hl}\\Delta E2_{hl}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()
gg<- gg+geom_text_repel()+theme(axis.text=element_text(size=12), axis.title=element_text(size=17,face="bold"))

plot(gg)
pdf("fit_a_01_luscher.pdf", width = 8, height = 5)
plot(gg)
dev.off()

###
```
## Comparison with PT

In perturbation theory we have 

$$ 
   a_{01} (m_0+m_1)=-\lambda/\pi =0.7957747
$$
```{r, echo=FALSE, results='asis'}
kable(df_tot_compact[,c("L","T","meff0","meff1","a_01_luscher","a_01_m0_m1") ])


```


## Comparing with BH method

$$C_4^{BH}=\frac{\langle \phi_0(\frac{T}{2})\phi_1(t)\phi_1(\frac{T}{8}) \phi_0(0)\rangle}
    {\langle \phi_0(\frac{T}{2}) \phi_0(0)\rangle \langle \phi_1(t)\phi_1(\frac{T}{8}) \rangle} -1$$
    
    

Fit function:
$$C_4^{BH}=\frac{1}{8m_0 m_1L^3} \left(8\pi(m_0+m_1) a_N (t-T/8) + 16 a_N a_N   \sqrt{ 2 \pi  (m_0+m_1)  m_0 m_1 (t-T/8) }\right)$$

    

```{r, echo=FALSE, warning=FALSE}

kable(df_tot_compact[,c("L","T","a_01_luscher", "a_01_BH") ])

gg <- ggplot(df, aes(x=L, y=a_01_BH ,label=T )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes(x=L, ymin=a_01_BH-a_01_BH_err, ymax=a_01_BH+a_01_BH_err),color="red", width=0.2)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$a_{01}^{BH}$') )
gg<- gg+xlim(9,41)+ ylim(-2,0)
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()
plot(gg)



```


## Adding a constant in BH method

$$C_4^{BH}=\frac{\langle \phi_0(\frac{T}{2})\phi_1(t)\phi_1(\frac{T}{8}) \phi_0(0)\rangle}
    {\langle \phi_0(\frac{T}{2}) \phi_0(0)\rangle \langle \phi_1(t)\phi_1(\frac{T}{8}) \rangle} $$
    
    

Fit function:
$$C_4^{BH}=\frac{1}{8m_0 m_1L^3} \left(8\pi(m_0+m_1) a_N (t-T/8) + 16 a_N a_N   \sqrt{ 2 \pi  (m_0+m_1)  m_0 m_1 (t-T/8) }+const  \right)$$

```{r, echo=FALSE, warning=FALSE}
kable(df_tot_compact[,c("L","T","a_01_luscher", "a_01_BH","a_01_BH_c") ])

colors <- c("a_01_BH" = "red", "a_01_BH+constant" = "darkgreen")

gg<- ggplot()
gg <-gg+ geom_point(data=df, aes(x=L, y=a_01_BH_c ,label=T,color="a_01_BH+constant" )  ) 
gg<- gg+ geom_text_repel(data=df, aes(x=L, y=a_01_BH_c ,label=T,color="a_01_BH+constant" ))
gg <- gg +geom_errorbar(data=df, aes(x=L, ymin=a_01_BH_c-a_01_BH_c_err, ymax=a_01_BH_c+a_01_BH_c_err,color="a_01_BH+constant"), width=0.2)
gg<- gg+geom_text_repel()

gg <- gg+geom_point(data=df, aes(x=L+0.5, y=a_01_BH ,label=T ,color="a_01_BH")  ) 
gg <- gg+geom_text_repel(data=df, aes(x=L+0.5, y=a_01_BH ,label=T ,color="a_01_BH")  ) 
gg <- gg +geom_errorbar(data=df, aes(x=L+0.5, ymin=a_01_BH-a_01_BH_err, ymax=a_01_BH+a_01_BH_err ,color="a_01_BH"), width=0.2)


#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$a_{01}^{BH}$') )
#gg<- gg+xlim(9,41)+ ylim(-0.005,1e-3)
gg <- gg+theme_bw()
gg<- gg+ labs( color = "Legend") +   scale_color_manual(values = colors)
gg<- gg+  coord_cartesian(ylim=c(-4,1))
plot(gg)



```




## Two $\phi_0$ particle energy and scattering length with Luscher method

$$
\langle \phi_0\phi_0 (t)  \phi_0\phi_0(0) \rangle= |A_{N\pi\to0}| \left(e^{-tE_{N\pi} }+ e^{-(T-t)E_{N\pi} }\right)+
|A_{\pi\to \pi}|^2  e^{-TE_\pi  }
$$
$$
\Delta E_2=E2_{01}-2m_{meff0} = -\frac{2\pi a }{\mu_{00}L^3}\left[1+c_1 \frac{a}{L}+c_2\left(\frac{a}{L}\right)^2\right]+ O\left(\frac{1}{L^6}\right)
$$
where $\mu_00=m_0/2$

```{r ,echo=FALSE, warning=FALSE,results='asis'}

kable(df_tot_compact[,c("L","T","E2_0","DeltaE2_0" ,"a_0_luscher") ])

gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=E2_0+0.5,label=T  )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes( ymin=E2_0-E2_0_err, ymax=E2_0+E2_0_err), width=0.002)

#gg<- gg+geom_point(aes(x=L+T*0.005-0.5, y=E2_01+0.4,label=T  ),color="blue") 
#gg <- gg +geom_errorbar(aes( ymin=E2_01-E2_01_err, ymax=E2_01+E2_01_err), width=0.002)
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$E2_{00}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

plot(gg)


gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=a_0_luscher,label=T  ) , color="blue" ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes( ymin=a_0_luscher-a_0_luscher_err, ymax=a_0_luscher+a_0_luscher_err), color="blue", width=0.2)  
#gg <- gg+labs( color = "Legend") +    scale_color_manual(values = colors)
gg <- gg+ labs(x = TeX('L'), y= TeX('$a_{ll}^{luscher}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()

gg<- gg+geom_text_repel()+theme(axis.text=element_text(size=12), axis.title=element_text(size=17,face="bold"))

plot(gg)
pdf("a_00_luscher.pdf", width = 8, height = 5)
plot(gg)
dev.off()

```



## Fitting all data

```{r,echo=FALSE}
xx<-df[,"L"]
yy<-df[,"muDE2_0"]*df[,"L"]^3
dy<-df[,"muDE2_0_err"]*df[,"L"]^3
c1<- -2.837297
c2<- 6.375183

wnlmod <- nls(yy ~ -(2*pi *a)*(1+c1*a/xx+c2*(a/xx)^2) , start = list(a = 1), weights = dy^-2, trace=TRUE)
res<-summary(wnlmod)$coefficients
kable(res)
gg <- ggplot(df, aes(x=L+T*0.005-0.5, y=muDE2_0*L^3,label=T  )  ) + geom_point(size=2) 
gg <- gg +geom_errorbar(aes( ymin=(muDE2_0-muDE2_0_err)*L^3, ymax=(muDE2_0+muDE2_0_err)*L^3, width=0.002)  ,color="blue", width=0.2)  
dx<-data.frame(xx=seq(min(df[,"L"]-2),max(df[,"L"]+2), length.out=50   ))
dx$v<-predict(wnlmod, newdata = dx)
gg <- gg+ geom_line(data=dx, aes(x=xx, y=v  ))
#gg <- gg+lines(xx, predict(wnlmod), col = "red")
gg <- gg+ labs(x = TeX('L'), y= TeX('$L^3\\mu_{00}\\Delta E2_{00}$') )
gg <- gg+theme_bw()
gg<- gg+geom_text_repel()+theme(axis.text=element_text(size=12), axis.title=element_text(size=17,face="bold"))

plot(gg)
pdf("fit_a_00_luscher.pdf", width = 8, height = 5)
plot(gg)
dev.off()

###
```


## Comparison with PT

In perturbation theory we have  for $\lambda=2.5$
$$ 
   a_{01} (m_0)=-3\lambda/(4\pi) =0.59683103659  
$$

```{r, echo=FALSE, results='asis'}

kable(df_tot_compact[,c("L","T","meff0","meff1","a_0_luscher", "a_00_m0") ] )


```